|

### 2022-04-18 Memo/memo.Rmd
edits to memo

In response to comments from Reviewer 1, we have revised our Methods section to
clarify our selection of independent variables, including the use of dummy
variables to improve the accuracy of our estimates, and to provide further
information about our online survey. Additionally, we have included a new
section in the Supplemental Materials to explain how our survey was conducted
and how they contribute to our results. We believe these addition also give the
paper a better theoretical frame to help readers sort through the (many)
results we present.

>>>>

In response to comments from Reviewer 1, we have revised our Methods section to
clarify our selection of independent variables, including the use of dummy
variables to improve the accuracy of our estimates, and to provide further
information about our online survey. Additionally, we have included a new
section in the Supplemental Materials to explain how we conducted our survey
and how it contributes to our results. We believe these addition also give the
paper a better theoretical frame to help readers sort through the (many)
results we present.
